Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-27 article.tex
minor change in appendix
minor changes in appendix

Two issues remain with this heuristic. First, it does not allow to detect a
directed relationship if both neurons are activated simultaneously at the same
time step, ie., when the delay between the two activations is below the time
resolution. Second, one needs to compare $s_{j,i}$ and $s_{i,j}$ to decide on
edge orientation. Indeed, edge orientation can only be predicted with some
confidence if either $s_{i,j}$ is greater than $s_{j,i}$ ($i\rightarrow j$) or
$s_{i,j}$ is lower than $s_{j,i}$ ($i\rightarrow j$). To address these issues,
we computed a differential pairwise coefficient $z_{ij}$ defined as follows:
\begin{align}
z_{ij} = \sum_{t=1}^{T - 1}
    \mathbb{1}((x_j^{t+1} - x_i^t) \in \left[\phi_1, \phi_2 \right]) -
    \mathbb{1}((x_i^{t+1} - x_j^t) \in \left[\phi_1, \phi_2 \right]),
\end{align}
where $T$ is the number of time steps, $\phi_1$ and $\phi_2$ are parameters.

@@

\begin{table}[h]
\centering
\small
\begin{tabular}{| l | c c c c c c |}
\hline
& \multicolumn{6}{c|}{AUROC}\\
\textit{Method} $\backslash$ \textit{normal-} & \textit{lowcon} & \textit{highcon} & \textit{lowcc} & \textit{highcc} & \textit{3-highrate} & \textit{4-lownoise} \\
\hline
\hline
Averaging     & 0.947 & 0.943 & 0.920 & 0.942 & 0.959 & 0.934 \\
Full method   &  &  &  & & &\\
PC & 0.782 & 0.920 &  0.846 & 0.897  & 0.898  & 0.873 \\
GTE & 0.846 & 0.905 & 0.848 & 0.899 & 0.905 & 0.879\\
GENIE3 & 0.781 &  0.922 & 0.875 & 0.899 & 0.886 &  0.890 \\ \hline
& \multicolumn{6}{c|}{AUPRC}\\ \hline
Averaging     & 0.320 & 0.429 & 0.262 & 0.478 & 0.443 & 0.412 \\
Full method   &  &  &  & & &\\
PC & 0.074 & 0.218 & 0.082 & 0.165  & 0.193 & 0.135 \\
GTE & 0.094 & 0.211 & 0.081 & 0.165 & 0.210 & 0.144\\
GENIE3 & 0.128 & 0.261 & 0.108 & 0.293 & 0.256 & 0.224\\ \hline
\end{tabular}
\caption{Performance (top: AUROC, bottom: AUPRC) on specific datasets with different methods.}
\label{tab:results_appendix}
\end{table}

>>>>

Two issues remain with this heuristic. First, it does not allow to detect a
directed relationship if both neurons are activated simultaneously at the same
time step, ie., when the delay between the two activations is below the time
resolution. Second, one needs to compare $s_{j,i}$ and $s_{i,j}$ to decide on
edge orientation. Indeed, edge orientation can only be predicted with some
confidence if either $s_{i,j}$ is greater than $s_{j,i}$ ($i\rightarrow j$) or
$s_{i,j}$ is lower than $s_{j,i}$ ($j\rightarrow i$). To address these issues,
we computed a differential pairwise coefficient $z_{ij}$ defined as follows:
\begin{align}
z_{ij} = \sum_{t=1}^{T - 1}
    \mathbb{1}((x_j^{t+1} - x_i^t) \in \left[\phi_1, \phi_2 \right]) -
    \mathbb{1}((x_i^{t+1} - x_j^t) \in \left[\phi_1, \phi_2 \right]),
\end{align}
where $T$ is the number of time steps, $\phi_1$ and $\phi_2$ are parameters.

@@

\begin{table}[h]
\caption{Performance (top: AUROC, bottom: AUPRC) on specific datasets with different methods.}
\label{tab:results_appendix}
\centering
\small
\begin{tabular}{| l | c c c c c c |}
\hline
& \multicolumn{6}{c|}{AUROC}\\
\textit{Method} $\backslash$ \textit{normal-} & \textit{lowcon} & \textit{highcon} & \textit{lowcc} & \textit{highcc} & \textit{3-highrate} & \textit{4-lownoise} \\
\hline
\hline
Averaging     & 0.947 & 0.943 & 0.920 & 0.942 & 0.959 & 0.934 \\
Full method   &  &  &  & & &\\
PC & 0.782 & 0.920 &  0.846 & 0.897  & 0.898  & 0.873 \\
GTE & 0.846 & 0.905 & 0.848 & 0.899 & 0.905 & 0.879\\
GENIE3 & 0.781 &  0.922 & 0.875 & 0.899 & 0.886 &  0.890 \\ \hline
& \multicolumn{6}{c|}{AUPRC}\\ \hline
Averaging     & 0.320 & 0.429 & 0.262 & 0.478 & 0.443 & 0.412 \\
Full method   &  &  &  & & &\\
PC & 0.074 & 0.218 & 0.082 & 0.165  & 0.193 & 0.135 \\
GTE & 0.094 & 0.211 & 0.081 & 0.165 & 0.210 & 0.144\\
GENIE3 & 0.128 & 0.261 & 0.108 & 0.293 & 0.256 & 0.224\\ \hline
\end{tabular}
\end{table}
